Concordance between observations and simulations in the evolution of the mass relation between supermassive black holes and their host galaxies

### 2022-03-28 projects/2020_HSC_to_numerical_simulation/manuscript/manuscript.tex
Some updates before change selection

%% The first piece of markup in an AASTeX v6.x document is the \documentclass
%% command. LaTeX will ignore any data that comes before this command. The 
%% documentclass can take an optional argument to modify the output style.
%% The command below calls the preprint style which will produce a tightly 
%% typeset, one-column, single-spaced document.  It is the default and thus
%% does not need to be explicitly stated.
%%
%% using aastex version 6.3
%\documentclass[linenumbers]{aastex631}
%\documentclass[twocolumn, linenumbers]{aastex631}
\documentclass[twocolumn]{aastex631}

@@

\def\smass{{$M_*$}}
\def\sersic{S\'ersic}
\def\halpha{${\rm H}\alpha$}
\def\hbeta{${\rm H}\beta$}
\def\mbh{$\mathcal M_{\rm BH}$}
\def\lcdm{$\Lambda$CDM}
\def\hst{{\it HST}}
\def\kms{km~s$^{\rm -1}$}

@@

\begin{abstract}
We carry out a comparative analysis of the relation between the mass of supermassive black holes (BHs) and the stellar mass of their host galaxies (\mbh -- \smass) at $0.2<z<1.7$ using well-matched observations and multiple state-of-the-art simulations (e.g., Massive Black II, Horizon-AGN, Illustris, TNG and a semi-analytic model). The observed sample consist of 646 uniformly-selected SDSS quasars ($0.2 < z < 0.8$) and 32 broad-line AGNs ($1.2<z<1.7$) with imaging from Hyper Suprime-Cam (HSC) for the former and Hubble Space Telescope (HST) for the latter. To make fair comparisons, we first add realistic observational uncertainties to the simulation data and then construct a simulated sample in the same manner as the observations. Over the full redshift range, our analysis demonstrates that all simulations predict a level of intrinsic scatter of the scaling relations comparable to the observations which appear to agree with the dispersion of the local relation. 
Regarding the mean scaling relation, Horizon-AGN and TNG are in closest agreement with the observational data at both low and high redshift ($z\sim$ 0.2 and 1.5, respectively) while the other simulations show subtle differences within the uncertainties. 
For insight into the physics involved, the scatter of the scaling relation, seen in the SAM, is reduced by a factor of two and thus closer to the observations after adopting a new feedback model which considers the geometry of the AGN outflow. The consistency in the dispersion with redshift in our analysis lends support to the importance of both quasar and radio mode feedback prescriptions in the simulations. Finally, we investigate evolution as a function of stellar and black hole mass, and argue that the most direct way to probe the co-evolution of galaxies and black holes is to increase the sensitivity, e.g., with JWST, thereby pushing to lower masses and minimizing possible biases arising from selection effects.

@@

\section{Introduction} \label{sec:intro}

The close correlations between supermassive black holes and the properties of their host galaxies (e.g., stellar mass) indicate a physical coupling during their joint evolution~\citep{Mag++98, F+M00, M+H03, H+R04, Gul++09}. To understand the nature of this connection, considerable efforts have been focused on measuring such correlations using broad-line active galactic nucleus (AGN) over a range of redshifts with the intention to determine how and when the correlation emerges and evolves over cosmic time \citep[e.g.,][]{Tre++04,Peng2006a, Tre++07, Woo++08, Jahnke2009, Bennert11, Schramm2013, Park15, Mechtley2016, Ding2020, 2021arXiv210902751L}. While, an {\it observed} evolution has been found in many studies in which the growth of BHs predates that of the host, other studies predict that BHs grow commensurately with galaxies.
However, to understand the significance {\it intrinsic} evolution, it is necessary to take into account systematic uncertainties and the selection effects~\citep{Tre++07, Lauer2007, Schulze2014, Park15}.

@@

Numerical simulations provide an opportunity to further understand the connection between BHs and their host galaxies. For example, a comparison of scaling relations has been made using state-of-the-art cosmological hydrodynamical simulation of structure formation ({\tt MassiveBlackII}) and observational measurements at  $0.3<z<1$ \citep[e.g., ][]{DeG++15}, which show a positive evolution (i.e., the mass growth of the BH growth predates that of its host). Further efforts are using large-volume simulations to investigate the scaling relations and find good agreement with the local relation with redshift evolution, 
including the Magneticum Pathfinder smooth-particle hydrodynamics (SPH) Simulations~\citep{Steinborn2015}, the Evolution and Assembly of Galaxies and their Environments~(EAGLE) suite of SPH simulations~\citep{Schaye2015}, Illustris moving-mesh simulation~\citep{Sijacki2015, 2014MNRAS.444.1518V, Li2019} and the SIMBA simulation~\citep{Thomas2019}. 
In particular, the \mbh-\smass\ relation using BH populations using six large-scale cosmological simulations (i.e, Illustris, TNG100, TNG300, Horizon-AGN, EAGLE, and SIMBA) has been compared with observations in the local universe in a recent study~\citep{Habouzit2021}. However, these comparison works are limited by the observation data in terms of the sample size ($<$100) and redshift range (i.e., limited to the local universe).

For such comparisons using simulations, it is crucial to consider the systematic uncertainties and selection biases. A direct means to account for these is to apply the same effects and selection to the simulation products and make a forward comparison in the observational plane. In~\citet{Ding2020b}, a direct comparison has been performed using 32 X-ray-selected AGN at $1.2<z<1.7$ and a direct comparison with two state-of-the-art simulation efforts, including {\tt MassiveBlackII} (MBII) and a Semi-analytic Model \citep[SAM,][]{Menci2014, Menci2016}. The dispersion in the mass ratio between black hole mass and stellar mass is significantly more consistent with the MBII prediction ($\sim0.3$~dex) favoring the hypothesis of AGN feedback being responsible for a causal link between the BH and its host galaxy.

@@

\subsection{SDSS/HSC sample}\label{sec:hsc}
A sample of $\sim$5000 type-1 SDSS quasars from the DR14 catalog~\citep{Paris2018} at $0.2<z<1$ has been imaged by the high-resolution Subaru Strategic Program (SSP) wide area survey~\citep{Aihara2019} using Hyper Suprime-Cam~\citep{Miyazaki2018}. With accurate PSF models in five optical bands {\it grizy}, two-dimensional quasar-host decompositions have been performed \citep[][hereafter L21a]{Li2021a} to obtain the flux and color of each quasar's host galaxy. The stare-of-the-art image modeling software {\tt lenstronomy} \citep{Birrer2015, Birrer2018, Birrer2021} is adopted to perform the modeling task. This approach is first developed by~\citet{Ding2020} and used to decompose the near-infrared emission of the HST sample (see next section). Having measured the host light in each band, the stellar mass of host galaxy is derived using spectral energy distribution (SED) fitting with CIGALE~\citep{Boquien2019}. Simulation tests are also performed to verify the fidelity of the \smass\ measurements. The statistical measurement error on \smass\ is at the $\sim$0.2~dex level. The values of \mbh\ are determined by~\citet{Rakshit2020} which are estimated based on the \hbeta-based measurements using the virial method~\citep{Peterson2004, Vestergaard2006}. The typical error of \mbh\ are estimated to be 0.4 dex. We refer the reader to~\citet{Li2021a} in the Section~4.2 for more details.

@@

\begin{deluxetable*}{lccccc}
\tablecaption{Key characteristics of hydrodynamic simulations used in this study.\label{tab:sim_sum}}
\tablewidth{0pt}
\tablehead{
\colhead{Simulation} & MBII & Illustris &  TNG100 & TNG300 & Horizon-AGN
}
\startdata
box sizes $(\mathrm{cMpc})^3$  & $142.7^3$ & $(106.5)^3$ & $(111)^3$ & $(302)^3$ & $(142)^3$ \\
particles  & $2\times1792^3$ & $2\times1820^3$ & $2\times1820^3$ & $2\times2500^3$ & $\sim2\times1024^3$ \\
\cline{1-6}
{\bf mass resolution} \\
 dark matter &$1.57\times10^7$ & $6.26\times10^6$ & $7.5\times10^6$ & $5.9\times10^7$ & $8\times10^7$ \\
 baryonic matter &$3.14\times10^6$ & $1.26\times10^6$ & $1.4\times10^6$ & $1.1\times10^7$ & $2\times10^6$ \\
\cline{1-6}
{\bf AGN feedback} & \multicolumn{2}{c}{(feedback efficiency $\times$ radiative efficiency)} \\
High acc. mode & 0.05 $\times$ 0.1 & 0.05 $\times$ 0.2 & 0.1 $\times$ 0.2 & 0.1 $\times$ 0.2 & 0.15 $\times$ 0.1 \\
Low acc. mode  & -- & 0.35 $\times$ 0.2 & $\leq0.2 \times$ 0.2 & $\leq0.2 \times$ 0.2 & 1 $\times$ 0.1 \\
Transitions btw. modes & -- & 0.05 & \multicolumn{2}{c}{min[$2\times10^{-3}(\frac{M_{\rm BH}}{10^8M_{\odot}})^2$, 10\%]} & 0.01 \\
\cline{1-6}
AGN fueling mechanism   & ${4\pi G^2 M_{BH}^2 \rho}/{(c_s^2+v_{BH}^2)^{3/2}}$ & $\alpha \dot{M}_{Bondi}$ & $\dot{M}_{Bondi}$&$\dot{M}_{Bondi}$ & $\alpha\dot{M}_{Bondi}$ \\
maximum accretion rate & 2 $\times$Edd. acc. rate & Edd. acc. rate & Edd. acc. rate & Edd. acc. rate & Edd. acc. rate\\
\enddata
\tablecomments{In the penultimate row, $\alpha$ is the boost factor. For Illustris, $\alpha = 100$; for Horizon-AGN, $\alpha =$ max$[(\rho/\rho_0)^2, 1]$. $\dot{M}_{Bondi}= 4\pi G^2M_{BH}^2 \rho/c_s^3$.
}
\end{deluxetable*}

\section{Simulations and comparison strategy}
\label{sec:simulations}
We introduce the simulation samples that are adopted in this section. All the simulation are based on the larger-scale cosmological simulations, except the Semianalytic Model (SAM) simulation (see Section~\ref{subsec:SAM}). In Table~\ref{tab:sim_sum}, we summarized the key elements for each hydrodynamic simulation being considered.

\subsection{{\tt MassiveBlackII} (MBII)}\label{subsec:MBII}
MBII is a high-resolution cosmological hydrodynamic simulation that has a box size of $(142.7~\mathrm{cMpc})^3$
and $2\times1792^3$ particles. The simulation is based on smooth particle hydrodynamic (SPH) code \texttt{P-GADGET}, a hybrid version of the parallel code {\tt GADGET}~\citep{2005MNRAS.364.1105S}. The base cosmology parameters are based on the WMAP7 results~\citep{2011ApJS..192...18K}. For dark matter and gas, the mass resolutions are $1.57\times 10^7~M_{\odot}$ and $3.14\times 10^6~M_{\odot}$, respectively. The simulation includes a full modeling of gravity plus gas hydrodynamics, with a wide range of subgrid recipes to model the star formation~\citep{2003MNRAS.339..289S}, BH growth, and the feedback process~\citep{2005Natur.433..604D}. Halos were identified using a friends-of-friends (FOF) group finder~\citep{1985ApJ...292..371D}. Galaxies are identified with the stellar matter components of subhalos; these subhalos are identified using {\tt SUBFIND} within the halos~\citep{2005MNRAS.364.1105S}.

To model supermassive black holes, a BH seed with mass $5\times 10^{5}~M_{\odot}/h$ are inserted into halos of mass $\gtrsim 5\times 10^{10}~M_{\odot}/h$. Once seeded, BH growth via gas accretion is assigned at a rate of $\dot{M}_{BH}={4\pi G^2 M_{BH}^2 \rho}/{(c_s^2+v_{BH}^2)^{3/2}}$ where $\rho$ and $c_s$ are the density and sound speed of the interstellar medium (ISM) gas at cold phase; $v_{BH}$ is the relative velocity between the BH and its surrounding gas. Note that unlike several previous works, the accretion rate in MBII adopt the prescription in~\citet{Pelupessy2007} which does not include any artificial boost factor. The accreted gas is released as radiation at a radiative efficiency of 10\%. A fraction of 5\% of the radiated energy thermally couples to the surrounding gas as black hole (or AGN) feedback~\citep{2005Natur.433..604D}. A mildly super-Eddington (two times Eddington rate) is allowed. Due to resolution limitations, BH dynamics cannot be self-consistently modeled in the simulations. Two BHs are considered to be merged when their separation distance is below the simulation spatial resolution (i.e., the SPH smoothing length) and their relative speeds are lower than the local sound speed of the medium.

@@

\subsection{Illustris}
The Illustris Project is another large scale hydrodynamics simulation, introduced in~\citet{2014MNRAS.444.1518V, 2014Natur.509..177V}. The simulation consist of a volume of (106.5 cMpc)$^3$~(slightly smaller than MassiveBlack II), 
and was run with the moving Voronoi mesh code {\tt Arepo}~\citep{2010MNRAS.401..791S} with a base cosmology adopted from WMAP9 results~\citep{2013ApJS..208...19H}. Besides gravity and gas hydrodynamics, the simulation calculates the astrophysical processes ~\citep{2013MNRAS.436.3031V, 2014MNRAS.438.1985T} that includes gas cooling and star formation~(with a density threshold of 0.13 cm$^{-3}$, \citealt{2003MNRAS.339..289S}), stellar evolution and chemical enrichment, kinetic stellar feedback by SNe activity, BH growth~(accretion and merging), and AGN feedback.

BHs are seeded with an initial mass of $1 \times 10^5~M_{\odot}/h$ when a halo exceeds a mass of $5 \times 10^{10}~M_{\odot}/h$. BHs then grow via accretion described by the Eddington limited Bondi-Hoyle-Lyttleton formalism ($\alpha4\pi G^2M_{BH}^2 \rho/c_s^3$), as well as mergers with other BHs. The boost factor $\alpha=100$ is introduced to account for the unresolved multiphase ISM~\citep{Springel2005, 2009MNRAS.398...53B}, which is otherwise expected to underestimate the density around the BHs. Lastly, accreting black holes radiate with a bolometric luminosity given by $\epsilon_r \dot{M}_{BH}c^2$, where $\dot{M}_{BH}$ is the mass accretion rate and $\epsilon_r=0.2$ is the radiative efficiency.

The AGN feedback consists of three components, namely quasar-mode, radio-mode and radiative feedback. In the quasar-mode which holds for BHs with Eddington ratio $>0.01$, the AGNs deposit $5\%$~(quasar-mode feedback efficiency) of their released energy into the surrounding gas as thermal energy. For Eddington ratios $<0.01$, the AGN feedback is in radio-mode where the thermal energy is released as hot bubbles with a radius of $\sim$ 100~kpc at~(irregular) intervals between which the BH mass grows by a fixed fraction. The energy of the bubbles is given by $\epsilon_m \epsilon_r \delta M_{bh} c^2$ where $\delta M_{bh}$ is the change in BH mass within the last time interval, and $\epsilon_m=0.35$ is the radio-mode feedback efficiency. Lastly, the radiative feedback mode is implemented by modifying the heating and cooling rates of the gas in the presence of radiation from all surrounding AGN. As in MBII, a 3D 30~kpc spherical aperture is used to obtained the galaxy stellar mass, assuming a \cite{2003PASP..115..763C} IMF.

\subsection{IllustrisTNG}
{\it The Next Generation Illustris Simulations} (IllustrisTNG)~\citep{2018MNRAS.475..676S, Pillepich2018} are a suite of magnetohydrodynamical simulations of galaxy formation in large cosmological volumes. It builds upon the scientific achievements of the Illustris simulation with improvements upon Illustris by 1) extending the mass range of the simulated galaxies and haloes, 2) adopting an improved numerical and astrophysical modeling, and 3) addressing the identified shortcomings of the previous generation simulations.

The TNG100 and TNG300 have a volume of (100~cMpc)$^3$ and (300~cMpc)$^3$, respectively. The adopted cosmological parameters are updates by the Planck result~\citep{2016A&A...594A..13P}.
The gas cooling and star formation prescriptions are broadly similar to the Illustris model. However significant updates have been made to the stellar feedback model~(more details in \citealt{2018MNRAS.473.4077P}).
BH seeds with initial mass of $8 \times 10^5 M_{\odot}/h$ are placed in Dark matter halos with a mass exceeding $5 \times 10^{10} M_{\odot}/h$. Notably, the seed mass is one order of magnitude higher than in the Illustris simulation. The BH accretion also follows the Bondi-Hoyle-Lyttleton formalism, but without any boost factor~(unlike Illustris). Accreting black holes release energy with a radiative efficiency of 0.2~(same as Illustris). The inclusion of the magnetic fields can affect the relationship between the BHs and their host galaxies properties; the \mbh-\smass\ mean relation is higher with magnetic fields~\citep{2018MNRAS.473.4077P}.

@@

\begin{figure*}
\centering
\begin{tabular}{c c}
{\includegraphics[trim = 0mm 0mm 65mm 10mm, clip, height=0.4\textwidth]{HSC_selection_MBII.png}}
{\includegraphics[trim = 0mm 0mm 20mm 10mm, clip,height=0.4\textwidth]{HST_selection_MBII.png}}
\end{tabular}
\caption{\label{fig:selection}Demonstration of AGN selection using MBII. {\it left}: Distribution of \mbh\ and Eddington ratio for the full (colored squares) MBII sample and individual objects meeting the observed selection criteria (blue circles). A matched HSC sample is shown by the orange data points. The light green background cloud shows the {\it intrinsic} simulated number density in this parameter space.
{\it right}: Similar to the panel on the left, this figure presents the impact of selection on the HST sample. For visual comparison between the HSC and HST selection, we show the region of the HST selection window in the left panel as dashed lines. 
}
\end{figure*}

>>>>

%% The first piece of markup in an AASTeX v6.x document is the \documentclass
%% command. LaTeX will ignore any data that comes before this command. The 
%% documentclass can take an optional argument to modify the output style.
%% The command below calls the preprint style which will produce a tightly 
%% typeset, one-column, single-spaced document.  It is the default and thus
%% does not need to be explicitly stated.
%%
%% using aastex version 6.3
%\documentclass[twocolumn, linenumbers]{aastex631}
\documentclass[twocolumn]{aastex631}

@@

\def\smass{{$M_*$}}
\def\sersic{S\'ersic}
\def\halpha{${\rm H}\alpha$}
\def\hbeta{${\rm H}\beta$}
\def\mbh{$M_{\rm BH}$}
\def\lcdm{$\Lambda$CDM}	
\def\hst{{\it HST}}
\def\kms{km~s$^{\rm -1}$}

@@

\begin{abstract}
We carry out a comparative analysis of the relation between the mass of supermassive black holes (BHs) and the stellar mass of their host galaxies (\mbh --\smass) at $0.2<z<1.7$ using well-matched observations and multiple state-of-the-art simulations (e.g., Massive Black II, Horizon-AGN, Illustris, TNG and a semi-analytic model). The observed sample consist of 646 uniformly-selected SDSS quasars ($0.2 < z < 0.8$) and 32 broad-line AGNs ($1.2<z<1.7$) with imaging from Hyper Suprime-Cam (HSC) for the former and Hubble Space Telescope (HST) for the latter. To make fair comparisons, we first add realistic observational uncertainties to the simulation data and then construct a simulated sample in the same manner as the observations. Over the full redshift range, our analysis demonstrates that all simulations predict a level of intrinsic scatter of the scaling relations comparable to the observations which appear to agree with the dispersion of the local relation. 
Regarding the mean scaling relation, Horizon-AGN and TNG are in closest agreement with the observational data at both low and high redshift ($z\sim$ 0.2 and 1.5, respectively) while the other simulations show subtle differences within the uncertainties. 
For insight into the physics involved, the scatter of the scaling relation, seen in the SAM, is reduced by a factor of two and thus closer to the observations after adopting a new feedback model which considers the geometry of the AGN outflow. The consistency in the dispersion with redshift in our analysis lends support to the importance of both quasar and radio mode feedback prescriptions in the simulations. Finally, we investigate evolution as a function of stellar and \red{BH} mass, and argue that the most direct way to probe the co-evolution of galaxies and \red{BH}s is to increase the sensitivity, e.g., with JWST, thereby pushing to lower masses and minimizing possible biases arising from selection effects.

@@

\section{Introduction} \label{sec:intro}
\todo{Re-read to avoid residual P1.}
The close correlations between \red{the mass of} supermassive black holes (\red{\mbh}) and the properties of their host galaxies (e.g., stellar mass\red{, \smass}) indicate a physical coupling during their joint evolution~\citep{Mag++98, F+M00, M+H03, H+R04, Gul++09}. To understand the nature of this connection, considerable efforts have been focused on measuring such correlations using broad-line active galactic nucleus (AGN) over a range of redshifts with the intention to determine how and when the correlation emerges and evolves over cosmic time \citep[e.g.,][]{Tre++04,Peng2006a, Tre++07, Woo++08, Jahnke2009, Bennert11, Schramm2013, Park15, Mechtley2016, Ding2020, 2021arXiv210902751L}. While, an {\it observed} evolution has been found \red{at redshift range xxx} in many studies \todo{move ref} in which the growth of BHs predates that of the host, other studies predict \todo{move ref} that BHs grow commensurately with galaxies.
However, to understand the significance {\it intrinsic} evolution, it is necessary to take into account systematic uncertainties and the selection effects~\citep{Tre++07, Lauer2007, Schulze2014, Park15}.

@@

Numerical simulations provide an opportunity to further understand the connection between BHs and their host galaxies. For example, a comparison of scaling relations has been made using state-of-the-art cosmological hydrodynamical simulation of structure formation ({\tt MassiveBlackII}) and observational measurements at  $0.3<z<1$ \citep[e.g., ][]{DeG++15}, which show a positive evolution (i.e., the mass growth of the BH growth predates that of its host). Further efforts are using large-volume simulations to investigate the scaling relations and find good agreement with the local relation with redshift evolution, 
including the Magneticum Pathfinder smooth-particle hydrodynamics (SPH) Simulations~\citep{Steinborn2015}, the Evolution and Assembly of Galaxies and their Environments~(EAGLE) suite of SPH \red{simulations~\citep{Schaye2015, Crain2015, McAlpine2016},} Illustris moving-mesh \red{simulation~\citep{Genel2014, 2014MNRAS.444.1518V, Sijacki2015, Nelson2015, Li2019}} and the SIMBA \red{simulation~\citep{Thomas2019, Dave2019}. }
In particular, the \mbh-\smass\ relation using BH populations using six large-scale cosmological simulations (i.e, Illustris, TNG100, TNG300, Horizon-AGN, EAGLE, and SIMBA) has been compared with observations in the local universe in a recent study~\citep{Habouzit2021}. However, these comparison works are limited by the observation data in terms of the sample size ($<$100) and redshift range (i.e., limited to the local universe).

For such comparisons using simulations, it is crucial to consider the systematic uncertainties and selection biases. A direct means to account for these is to apply the same effects and selection to the simulation products and make a forward comparison in the observational plane. In~\citet{Ding2020b}, a direct comparison has been performed using 32 X-ray-selected AGN at $1.2<z<1.7$ and a direct comparison with two state-of-the-art simulation efforts, including {\tt MassiveBlackII} (MBII) and a Semi-analytic Model \citep[SAM,][]{Menci2014, Menci2016}. The dispersion in the mass ratio between \red{BH} mass and stellar mass is significantly more consistent with the MBII prediction ($\sim0.3$~dex) favoring the hypothesis of AGN feedback being responsible for a causal link between the BH and its host galaxy.

@@

\subsection{SDSS/HSC sample}\label{sec:hsc}
A sample of $\sim$5000 type-1 SDSS quasars from the DR14 catalog~\citep{Paris2018} at $0.2<z<1$ has been imaged by the high-resolution Subaru Strategic Program (SSP) wide area survey~\citep{Aihara2019} using Hyper Suprime-Cam~\citep{Miyazaki2018}. With accurate PSF models in five optical bands {\it grizy}, two-dimensional quasar-host decompositions have been \red{performed \citep[][]{Li2021a}} to obtain the flux and color of each quasar's host galaxy. The stare-of-the-art image modeling software {\tt lenstronomy} \citep{Birrer2015, Birrer2018, Birrer2021} is adopted to perform the modeling task. This approach is first developed by~\citet{Ding2020} and used to decompose the near-infrared emission of the HST sample (see next section). Having measured the host light in each band, the stellar mass of host galaxy is derived using spectral energy distribution (SED) fitting with CIGALE~\citep{Boquien2019}. Simulation tests are also performed to verify the fidelity of the \smass\ measurements. The statistical measurement error on \smass\ is at the $\sim$0.2~dex level. The values of \mbh\ are determined by~\citet{Rakshit2020} which are estimated based on the \hbeta-based measurements using the virial method~\citep{Peterson2004, Vestergaard2006}. The typical error of \mbh\ are estimated to be 0.4 dex. We refer the reader to~\citet{Li2021a} in the Section~4.2 for more details.

@@

\begin{deluxetable*}{lccccc}
\tablecaption{Key characteristics of hydrodynamic simulations used in this study.\label{tab:sim_sum}}
\tablewidth{0pt}
\tablehead{
\colhead{Simulation} & MBII & Illustris &  TNG100 & TNG300 & Horizon-AGN
}
\startdata
box sizes $(\mathrm{cMpc})^3$  & $142.7^3$ & $(106.5)^3$ & $(111)^3$ & $(302)^3$ & $(142)^3$ \\
particles  & $2\times1792^3$ & $2\times1820^3$ & $2\times1820^3$ & $2\times2500^3$ & $\sim2\times1024^3$ \\
\cline{1-6}
{\bf mass resolution} \\
 dark matter &$1.57\times10^7$ & $6.26\times10^6$ & $7.5\times10^6$ & $5.9\times10^7$ & $8\times10^7$ \\
 baryonic matter &$3.14\times10^6$ & $1.26\times10^6$ & $1.4\times10^6$ & $1.1\times10^7$ & $2\times10^6$ \\
\cline{1-6}
{\bf AGN feedback} & \multicolumn{2}{c}{(feedback efficiency $\times$ radiative efficiency)} \\
High acc. mode & 0.05 $\times$ 0.1 & 0.05 $\times$ 0.2 & 0.1 $\times$ 0.2 & 0.1 $\times$ 0.2 & 0.15 $\times$ 0.1 \\
Low acc. mode  & -- & 0.35 $\times$ 0.2 & $\leq0.2 \times$ 0.2 & $\leq0.2 \times$ 0.2 & 1 $\times$ 0.1 \\
Transitions btw. modes & -- & 0.05 & \multicolumn{2}{c}{min[$2\times10^{-3}(\frac{M_{\rm BH}}{10^8M_{\odot}})^2$, 10\%]} & 0.01 \\
\cline{1-6}
AGN fueling mechanism   & ${4\pi G^2 M_{BH}^2 \rho}/{(c_s^2+v_{BH}^2)^{3/2}}$ & $\alpha \dot{M}_{Bondi}$ & $\dot{M}_{Bondi}$&$\dot{M}_{Bondi}$ & $\alpha\dot{M}_{Bondi}$ \\
maximum accretion rate & 2 $\times$Edd. acc. rate & Edd. acc. rate & Edd. acc. rate & Edd. acc. rate & Edd. acc. rate\\
\enddata
\tablecomments{In the penultimate row, $\alpha$ is the boost factor. For Illustris, $\alpha = 100$; for Horizon-AGN, $\alpha =$ max$[(\rho/\rho_0)^2, 1]$. $\dot{M}_{Bondi}= 4\pi G^2M_{BH}^2 \rho/c_s^3$. \todo{The $\leq$ sign in the low accretion feedback mode of TNG is also not clear. Is it a fixed value or a distribution?} \todo{Please mention whether the same radiative efficiency is used to compute AGN luminosity in all the simulations.}
}
\end{deluxetable*}

\section{Simulations and comparison strategy}
\todo{Uniform the descriptions of the simulations to lack homogeneity. (Illustris has star formation threshold). Re-write the section and provide the same information}
\label{sec:simulations}
We introduce the simulation samples that are adopted in this section. All the simulation are based on the larger-scale cosmological simulations, except the Semianalytic Model (SAM) simulation (see Section~\ref{subsec:SAM}). In Table~\ref{tab:sim_sum}, we summarized the key elements for each hydrodynamic simulation being considered.

\subsection{{\tt MassiveBlackII} (MBII)}\label{subsec:MBII}
MBII is a high-resolution cosmological hydrodynamic simulation that has a box size of $(142.7~\mathrm{cMpc})^3$
and $2\times1792^3$ particles. \todo{answer what is the factor 2 here. A twin box with 1793$^3$ each?} The simulation is based on smooth particle hydrodynamic (SPH) code \texttt{P-GADGET}, a hybrid version of the parallel code {\tt GADGET}~\citep{2005MNRAS.364.1105S}. The base cosmology parameters are based on the WMAP7 results~\citep{2011ApJS..192...18K}. For dark matter and gas, the mass resolutions are $1.57\times 10^7~M_{\odot}$ and $3.14\times 10^6~M_{\odot}$, respectively. The simulation includes a full modeling of gravity plus gas hydrodynamics, with a wide range of subgrid recipes to model the star formation~\citep{2003MNRAS.339..289S}, BH growth, and the feedback process~\citep{2005Natur.433..604D}. Halos were identified using a friends-of-friends (FOF) group finder~\citep{1985ApJ...292..371D}. Galaxies are identified with the stellar matter components of subhalos; these subhalos are identified using {\tt SUBFIND} within the halos~\citep{2005MNRAS.364.1105S}.

To model supermassive \red{BH, the initial} seed with mass $5\times 10^{5}~M_{\odot}/h$ are inserted into halos of mass $\gtrsim 5\times 10^{10}~M_{\odot}/h$. Once seeded, BH growth via gas accretion is assigned at a rate of $\dot{M}_{BH}={4\pi G^2 M_{BH}^2 \rho}/{(c_s^2+v_{BH}^2)^{3/2}}$ where $\rho$ and $c_s$ are the density and sound speed of the interstellar medium (ISM) gas at cold phase; $v_{BH}$ is the relative velocity between the BH and its surrounding gas. Note that unlike several previous works, the accretion rate in MBII adopt the prescription in~\citet{Pelupessy2007} which does not include any artificial boost factor. The accreted gas is released as radiation at a radiative efficiency of 10\%. A fraction of 5\% of the radiated energy thermally couples to the surrounding gas as \red{BH} (or AGN) feedback~\citep{2005Natur.433..604D}. A mildly super-Eddington (two times Eddington rate) is allowed. Due to resolution limitations, BH dynamics cannot be self-consistently modeled in the simulations. Two BHs are considered to be merged when their separation distance is below the simulation spatial resolution (i.e., the SPH smoothing length) and their relative speeds are lower than the local sound speed of the medium.

@@

\subsection{Illustris}
The Illustris Project is another large scale hydrodynamics simulation, introduced \red{in~\citet{Genel2014, 2014MNRAS.444.1518V, 2014Natur.509..177V, Sijacki2015, Nelson2015}.} The simulation consist of a volume of (106.5 cMpc)$^3$~(slightly smaller than MassiveBlack II), 
and was run with the moving Voronoi mesh code {\tt Arepo}~\citep{2010MNRAS.401..791S} with a base cosmology adopted from WMAP9 results~\citep{2013ApJS..208...19H}. Besides gravity and gas hydrodynamics, the simulation calculates the astrophysical processes ~\citep{2013MNRAS.436.3031V, 2014MNRAS.438.1985T} that includes gas cooling and star formation~(with a density threshold of 0.13 cm$^{-3}$, \citealt{2003MNRAS.339..289S}), stellar evolution and chemical enrichment, kinetic stellar feedback by SNe activity, BH growth~(accretion and merging), and AGN feedback.

BHs are seeded with an initial mass of $1 \times 10^5~M_{\odot}/h$ when a halo exceeds a mass of $5 \times 10^{10}~M_{\odot}/h$. BHs then grow via accretion described by the Eddington limited Bondi-Hoyle-Lyttleton formalism ($\alpha4\pi G^2M_{BH}^2 \rho/c_s^3$), as well as mergers with other BHs. The boost factor $\alpha=100$ is introduced to account for the unresolved multiphase ISM~\citep{Springel2005, 2009MNRAS.398...53B}, which is otherwise expected to underestimate the density around the BHs. Lastly, accreting \red{BH}s radiate with a bolometric luminosity given by $\epsilon_r \dot{M}_{BH}c^2$, where $\dot{M}_{BH}$ is the mass accretion rate and $\epsilon_r=0.2$ is the radiative efficiency.

The AGN feedback consists of three components, namely quasar-mode, radio-mode and radiative feedback. In the quasar-mode which holds for BHs with Eddington ratio $>0.01$, the AGNs deposit $5\%$~(quasar-mode feedback efficiency) of their released energy into the surrounding gas as thermal energy. For Eddington ratios $<0.01$, the AGN feedback is in radio-mode where the thermal energy is released as hot bubbles with a radius of $\sim$ 100~kpc at~(irregular) intervals between which the BH mass grows by a fixed fraction. The energy of the bubbles is given by $\epsilon_m \epsilon_r \delta M_{BH} c^2$ where $\delta M_{BH}$ is the change in BH mass within the last time interval, and $\epsilon_m=0.35$ is the radio-mode feedback efficiency. Lastly, the radiative feedback mode is implemented by modifying the heating and cooling rates of the gas in the presence of radiation from all surrounding AGN. As in MBII, a 3D 30~kpc spherical aperture is used to obtained the galaxy stellar mass, assuming a \cite{2003PASP..115..763C} IMF.

\subsection{IllustrisTNG}
{\it The Next Generation Illustris Simulations} \red{(IllustrisTNG)~\citep{2018MNRAS.475..676S, Pillepich2018, Naiman2018, Marinacci2018, Nelson2018}} are a suite of magnetohydrodynamical simulations of galaxy formation in large cosmological volumes. It builds upon the scientific achievements of the Illustris simulation with improvements upon Illustris by 1) extending the mass range of the simulated galaxies and haloes, 2) adopting an improved numerical and astrophysical modeling, and 3) addressing the identified shortcomings of the previous generation simulations.

The TNG100 and TNG300 have a volume of (100~cMpc)$^3$ and (300~cMpc)$^3$, respectively. The adopted cosmological parameters are updates by the Planck result~\citep{2016A&A...594A..13P}.
The gas cooling and star formation prescriptions are broadly similar to the Illustris model. However significant updates have been made to the stellar feedback model~(more details in \citealt{2018MNRAS.473.4077P}).
BH seeds with initial mass of $8 \times 10^5 M_{\odot}/h$ are placed in Dark matter halos with a mass exceeding $5 \times 10^{10} M_{\odot}/h$. Notably, the seed mass is one order of magnitude higher than in the Illustris simulation. The BH accretion also follows the Bondi-Hoyle-Lyttleton formalism, but without any boost factor~(unlike Illustris). Accreting \red{BH}s release energy with a radiative efficiency of 0.2~(same as Illustris). The inclusion of the magnetic fields can affect the relationship between the BHs and their host galaxies properties; the \mbh-\smass\ mean relation is higher with magnetic fields~\citep{2018MNRAS.473.4077P}.

@@

\begin{figure*}
\centering
\begin{tabular}{c c}
{\includegraphics[trim = 0mm 0mm 65mm 10mm, clip, height=0.4\textwidth]{HSC_selection_MBII.png}}
{\includegraphics[trim = 0mm 0mm 20mm 10mm, clip,height=0.4\textwidth]{HST_selection_MBII.png}}
\end{tabular}
\caption{\label{fig:selection}Demonstration of AGN selection using MBII. {\it left}: Distribution of \mbh\ and Eddington ratio for the full (colored squares) MBII sample and individual objects meeting the observed selection criteria (blue circles). A matched HSC sample is shown by the orange data points. The light green background cloud shows the {\it intrinsic} simulated number density in this parameter space.
{\it right}: Similar to the panel on the left, this figure presents the impact of selection on the HST sample. For visual comparison between the HSC and HST selection, we show the region of the HST selection window in the left panel as dashed lines. \todo{No mention of the redshift in Fig.2}
}
\end{figure*}
